---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# airnow

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/airnow)](https://CRAN.R-project.org/package=airnow)
[![R-CMD-check](https://github.com/briandconnelly/airnow/workflows/R-CMD-check/badge.svg)](https://github.com/briandconnelly/airnow/actions)
[![Codecov test coverage](https://codecov.io/gh/briandconnelly/airnow/branch/main/graph/badge.svg)](https://app.codecov.io/gh/briandconnelly/airnow?branch=main)
<!-- badges: end -->

airnow is an [R](https://www.r-project.org/) package for querying and retrieving air quality information from [AirNow](https://www.airnow.gov/) via the [AirNow API](https://docs.airnowapi.org/).
Current and historical readings as well as forecasts can be retrieved as tidy data frames.


## Installation

You can install the stable version of airnow from CRAN:

```{r, eval=FALSE}
install.packages("airnow")
```

If you'd like to try out the development version of airnow, you can install directly from GitHub:

```{r, eval=FALSE}
# install.packages("remotes")
remotes::install_github("briandconnelly/airnow")
```


## Creating an API Key

The [AirNow API](https://docs.airnowapi.org/) is generally free to use.
The `set_airnow_key()` function can be used to help you create and configure your API key.

```{r, eval=FALSE}
library(airnow)

set_airnow_key()
```


## Examples

### Current air quality in Seattle

The AirNow API allows you to query air conditions either by ZIP code or latitude/longitude.
Here, we’ll get the current conditions in Seattle by ZIP code:

```{r}
library(airnow)

get_airnow_observations(zip = "98101")
```


### Tomorrow's forecast for Napa, by reporting area

Every location belongs to an AirNow *reporting area*. The bundled `airnow_areas` table lists them, and `get_airnow_reporting_area()` finds the one for a ZIP code or coordinate pair.

```{r}
get_airnow_reporting_area(zip = "94558")

get_airnow_forecasts(area = "ca064")
```


### Find the site with the lowest air quality near Washington state

```{r message=FALSE}
library(airnow)
library(dplyr)

get_airnow_monitors(
  box = c(-125.394211, 45.295897, -116.736984, 49.172497),
  verbose = TRUE
) |>
  slice_max(order_by = aqi, n = 1) |>
  select(site_name, site_agency, latitude, longitude, aqi, datetime_observed)
```


## Disclaimer

This package and its author are not affiliated with [AirNow](https://www.airnow.gov/) or its [partners](https://www.airnow.gov/partners/).
See the [Data Exchange Guidelines](https://docs.airnowapi.org/docs/DataUseGuidelines.pdf) for more details about this data set and how it should be used.
Data are typically refreshed once per hour.
Please be kind to this service and limit your request rate.
