---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# airnow

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/airnow)](https://CRAN.R-project.org/package=airnow)
[![R-CMD-check](https://github.com/briandconnelly/airnow/workflows/R-CMD-check/badge.svg)](https://github.com/briandconnelly/airnow/actions)
[![Codecov test coverage](https://codecov.io/gh/briandconnelly/airnow/branch/main/graph/badge.svg)](https://app.codecov.io/gh/briandconnelly/airnow?branch=main)
<!-- badges: end -->

airnow is an [R](https://www.r-project.org/) package for querying and retrieving air quality information from [AirNow](https://www.airnow.gov/) via the [AirNow API](https://docs.airnowapi.org/).
Current and historical readings as well as forecasts can be retrieved as tidy data frames.


## Installation

airnow is still changing quite a bit, so it isn't quite ready for CRAN.
You can install the development version of airnow with:

```{r, eval=FALSE}
# install.packages("remotes")
remotes::install_github("briandconnelly/airnow")
```


## Creating an API Token

The [AirNow API](https://docs.airnowapi.org/) is generally free to use.
The `set_airnow_token()` function can be used to help you create and configure your API token.

```{r, eval=FALSE}
library(airnow)

set_airnow_token()
```


## Current Air Quality in Seattle

The AirNow API allows you to query air conditions either by ZIP code or latitude/longitude.
Here, we’ll get the current conditions in Seattle by ZIP code as a data frame:

```{r}
library(airnow)

get_airnow_conditions(zip = "98101")
```

If [tibble](https://CRAN.R-project.org/package=tibble) is installed, airnow's `get_airnow_` functions will return `tbl_df`s.


## Disclaimer

This package and its author are not affiliated with [AirNow](https://www.airnow.gov/) or its [partners](https://www.airnow.gov/partners/).
See the [Data Exchange Guidelines](https://docs.airnowapi.org/docs/DataUseGuidelines.pdf) for more details about this data set and how it should be used.
Please be kind to this service and limit your request rate.
Data are typically refreshed once per hour.
